Publication Bias in Meta-Analysis

### 2019-05-20 Presentation/present.Rnw
Presentation update

@@

dat_text <- data.frame(
  label = paste(c(sum(metac.cont$begg.test), sum(metac.cont$egger.test), sum(metac.cont$thomson.test)), "< 0.05"),
  test.type   = c("pval.begg.cont", "pval.egger.cont", "pval.thomson.cont"))

p.dist.cont <- metac.cont %>% ungroup() %>% 
  select(pval.egger.cont, pval.thomson.cont, pval.begg.cont) %>% 
  gather(key = "test.type", value = "p.value") %>% 
  ggplot(aes(x = p.value)) + geom_histogram(bins = 20) + theme_bw() + facet_wrap(~test.type) + 
	geom_text(data = dat_text, mapping = aes(x = -Inf, y = -Inf, label = label), hjust   = -1,
  vjust   = -4, color = "white")

dat_text <- data.frame(
  label = paste(c(sum(metac.bin$egger.test), sum(metac.bin$harbord.test), sum(metac.bin$peter.test), 
  										sum(metac.bin$rucker.test), sum(metac.bin$schwarzer.test)), "< 0.05"),
  test.type   = c("pval.egger.bin", "pval.harbord.bin", "pval.peter.bin", "pval.rucker.bin", "pval.schwarzer.bin"))

p.dist.bin <- metac.bin %>% ungroup() %>% 
  select(pval.egger.bin, pval.harbord.bin, pval.peter.bin, pval.rucker.bin, pval.schwarzer.bin) %>% 
  gather(key = "test.type", value = "p.value") %>% 
  ggplot(aes(x = p.value)) + geom_histogram(bins = 20) + theme_bw() + facet_wrap(~test.type) + 
	geom_text(data = dat_text, mapping = aes(x = -Inf, y = -Inf, label = label), hjust   = -0.65,
  vjust   = -2, color = "white")

@@

#Adjustment results: Effect difference histograms
effect.diff <- metac %>% mutate(
	est.fixef = ifelse(!is.na(est.fixef.bin), est.fixef - 1, est.fixef),
	est.ranef = ifelse(!is.na(est.fixef.bin), est.ranef - 1, est.ranef),
	est.trimfill.fixef = ifelse(!is.na(est.fixef.bin), est.trimfill.fixef - 1, est.trimfill.fixef),
	est.copas = ifelse(!is.na(est.fixef.bin), est.copas - 1, est.copas),
	est.reg.ranef = ifelse(!is.na(est.fixef.bin), est.reg.ranef - 1, est.reg.ranef),
	fixef.trimfill = ifelse(abs(est.fixef) > abs(est.trimfill.fixef), "Reduction", "Amplification"),
	fixef.copas = ifelse(abs(est.fixef) > abs(est.copas), "Reduction", "Amplification"),
	fixef.reg = ifelse(abs(est.fixef) > abs(est.reg.ranef), "Reduction", "Amplification"),
	fixef.trimfill.s = ifelse(sign(est.fixef) == sign(est.trimfill.fixef), "Unchanged", "Reversed"),
	fixef.copas.s = ifelse(sign(est.fixef) == sign(est.copas), "Unchanged", "Reversed"),
	fixef.reg.s = ifelse(sign(est.fixef) == sign(est.reg.ranef), "Unchanged", "Reversed"))

@@

hist.trimfill1 <- effect.diff %>% ggplot(aes(x = abs(est.fixef - est.trimfill.fixef))) +
	geom_histogram() + facet_grid(~factor(fixef.trimfill)) + xlim(0, 2)+ xlab("Effect difference") +
	geom_text(data = trimfill.label, mapping = aes(label = label, x = 0, hjust = 0.05, y = 300), 
						color = "black") + theme_bw() + 
	theme(legend.position = "bottom", strip.text.x = element_text(size=15))

@@

copas.label$label <- as.character(copas.label$label)
copas.label$label[1] <- sub("3.5,", "3.5, \n   ", copas.label$label[1])

@@

hist.copas1 <- effect.diff %>% filter(!is.na(est.copas)) %>% ggplot(aes(x = abs(est.fixef - est.copas))) +
	geom_histogram() + facet_grid(~factor(fixef.copas)) + xlim(0, 2) + xlab("Effect difference") +
	geom_text(data = copas.label, mapping = aes(label = label, x = 0, hjust = 0.05, y = 175), 
						color = "black") + theme_bw() +
	theme(legend.position = "bottom", strip.text.x = element_text(size=15))

@@

hist.reg <- effect.diff %>% ggplot(aes(x = abs(est.fixef - est.reg.ranef), fill = factor(fixef.reg.s))) +
	geom_histogram() + facet_grid(~factor(fixef.reg)) + xlim(0, 3)+ xlab("Effect difference") +
	geom_text(data = reg.ranef.label, mapping = aes(label = label, x= 0, y = 250, hjust = 0.05), 
						color = "black", size = 2.8) + theme_bw() + scale_fill_discrete(name="Effect direction") +
	theme(legend.position = "bottom", strip.text.x = element_text(size=15))

hist.reg1 <- effect.diff %>% ggplot(aes(x = abs(est.fixef - est.reg.ranef))) +
	geom_histogram() + facet_grid(~factor(fixef.reg)) + xlim(0, 3)+ xlab("Effect difference") +
	geom_text(data = reg.ranef.label, mapping = aes(label = label, x= 0, y = 250, hjust = 0.05), 
						color = "black", size = 2.8) + theme_bw() + 
	theme(legend.position = "bottom", strip.text.x = element_text(size=15))

@@

@@

#Scatterplots of metac-analysis and corrected log estimates
copas.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.fixef))), y = log(abs(est.copas)))) + geom_point() + 
	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
	xlab("Fixed effects log estimate") + ylab("Copas log estimate") + ggtitle("Fixed effects to Copas")

copas.ranef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.ranef))), y = log(abs(est.copas)))) + geom_point() + 
	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE, show.legend = T) + 
	xlab("Random effects log estimate") + ylab("Copas log estimate") + ggtitle("Random effects to Copas")

#Scatterplots of metac-analysis and corrected log estimates
reg.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs(log(abs((est.fixef))))), y = log(abs(log(abs(est.reg.ranef)))))) + geom_point() + 
	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
	xlab("Fixed effects log estimate") + ylab("Regression log estimate") + ggtitle("Fixed effects to Regression")

@@

@@

reg.ranef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.ranef), y = abs(zval.reg.ranef))) + geom_point() +
	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
	ggtitle("Random effects and Regression z statistics") + ylab("Regression  statistic") + xlab("Random effects  statistic")
@

@@

@@

\begin{frame}{Small Study Effects}
Causes:
\begin{itemize}
\item Selective publication of studies with significant results - publication bias
\item Selective reporting of most favorable outcomes
\item Systematical differences in study settings
\end{itemize}
\end{frame}

\begin{frame}{Small Study Effect Tests}
Tests applicable if:
\begin{itemize}
\item Number of studies $n$ large
\item variation in the estimated variances of effects %\\(here: $\frac{\sigma_{\textrm{max}}}{\sigma_{\textrm{min}}} > 4$)
\end{itemize}
Adjustments required if variance is dependent on effect size (e.g. log odds ratios)
\end{frame}

\begin{frame}[fragile]{Small Study Effect Tests}
Funnel plots (continuous outcome examples):

\vspace{-1.2cm}

<<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
par(las = 1, mfrow = c(1, 2))
funnel(meta.example)
funnel(meta.nexample)
@

\begin{frame}[fragile]{Regression based Tests}
Radial plots (continuous outcome examples):

<<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
par(las = 1, mfrow = c(1,2))
biased.rev$inv <- 1/biased.rev$se
plot(y = (biased.rev$effect/biased.rev$se), x = (biased.rev$se^-1), xlim = c(0, 6), xlab = "inverse standard error", 
		 ylab = "mean diff. / std. error")

unbiased.rev$inv <- 1/unbiased.rev$se
plot(y = (unbiased.rev$effect/unbiased.rev$se), x = (unbiased.rev$inv), xlim = c(0, 1.2), 
		 ylim = c(-18, 0), xlab = "inverse standard error", ylab = "mean diff. / std. error")
@

@@

\begin{frame}[fragile]{Shrinkage Regression}
Funnel plot with effect with infinite precision:

@@

\begin{frame}{Copas selection model}
\citet{Copas1}: Bivariate normal model with two parts:

@@

\begin{frame}{Trim-and-Fill}
Non-parametric, iterative method:

Cut away smallest study until funnel plot is symmetric

Mirror studies that are responsible for asymmetry
\end{frame}

@@

\vspace{-3mm}
<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
plot(hist.trimfill1)
@
\end{frame}

@@

\vspace{-3mm}
<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
plot(hist.copas1)
@
\end{frame}

@@

\vspace{-3mm}
<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
plot(hist.reg1)
@
\end{frame}

@@

\vspace{-3mm} 
<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
grid.arrange(trimfill.fixef.sc.zval, trimfill.ranef.sc.zval, ncol = 2)
@
\end{frame}

@@

\vspace{-3mm}
<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
grid.arrange(copas.fixef.sc.zval, copas.ranef.sc.zval, ncol = 2)
@
\end{frame}

@@

\vspace{-3mm}
<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
grid.arrange(reg.fixef.sc.zval, reg.ranef.sc.zval, ncol = 2)
@
\end{frame}

@@

>>>>

meta.id <- function(meta.id.tolook){
	dt <- data.ext %>% filter(meta.id == meta.id.tolook)
	if(any(is.na(dt$events1)) | all(dt$events1 == 0)){
		meta.ex <- metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2, studlab = study.name, data = dt)
	} else{
		meta.ex <- metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, studlab = study.name, sm = "RR", data = dt, method = "Inverse")
	}
	return(meta.ex)
}

funnel.id <- function(meta.id.tolook){
	funnel(meta.id(meta.id.tolook))
}

trimfill.id <- function(meta.id.tolook){
	funnel(trimfill(meta.id(meta.id.tolook)))
}

limitmeta.id <- function(meta.id.tolook){
	funnel(limitmeta(meta.id(meta.id.tolook)))
}

copas.id <- function(meta.id.tolook){
	auto.copas(meta.id(meta.id.tolook), 0.1)
}

setting.id <- function(meta.id.tolook){
	return(meta %>% filter(meta.id == meta.id.tolook) %>% select(comparison.name, comparison.nr, outcome.name, sungroup.name))
}

est.id <- function(meta.id.tolook){
	return(meta %>% filter(meta.id == meta.id.tolook) %>% select(est.fixef, est.ranef, est.copas, est.trimfill.fixef, est.reg.ranef))
}

single.study.id <- function(meta.id.tolook){
	return(print(data.ext %>% filter(meta.id == meta.id.tolook) %>% select(study.name, effect, se, total1, total2, events1, events2, mean1, mean2) %>% 
							 	arrange(se), n = 200))
}

@@

dat_text <- data.frame(
  label = paste(c(sum(metac.cont$begg.test), sum(metac.cont$egger.test), sum(metac.cont$thomson.test)), "< 0.05,",
  							round(c(mean(metac.cont$begg.test), mean(metac.cont$egger.test), mean(metac.cont$thomson.test)),2)*100, "%"),
  test.type   = c("pval.begg.cont", "pval.egger.cont", "pval.thomson.cont"))

labels <- c(pval.begg.cont = "Begg Mazumdar", pval.egger.cont = "Egger", pval.thomson.cont = "Thompson Sharp")
p.dist.cont <- metac.cont %>% ungroup() %>% 
  select(pval.egger.cont, pval.thomson.cont, pval.begg.cont) %>% 
  gather(key = "test.type", value = "p.value") %>% 
  ggplot(aes(x = p.value)) + geom_histogram(bins = 20) + theme_bw() + 
	facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 25, label = label),  color = "black") + 
	theme(strip.text.x = element_text(size=15))

	dat_text <- data.frame(
  label = paste(c(sum(metac.bin$harbord.test), sum(metac.bin$peter.test), 
  										sum(metac.bin$rucker.test), sum(metac.bin$schwarzer.test)), "< 0.05,",
  							round(c(mean(metac.bin$harbord.test), mean(metac.bin$peter.test), 
  										mean(metac.bin$rucker.test), mean(metac.bin$schwarzer.test)),2)*100, "%"),
  test.type   = c("pval.harbord.bin", "pval.peter.bin", "pval.rucker.bin", "pval.schwarzer.bin"))

labels <- c(pval.harbord.bin = "Harbord", pval.peter.bin = "Peter", pval.rucker.bin = "Rucker", pval.schwarzer.bin = "Schwarzer")

p.dist.bin <- metac.bin %>% ungroup() %>% 
  select(pval.harbord.bin, pval.peter.bin, pval.rucker.bin, pval.schwarzer.bin) %>% 
  gather(key = "test.type", value = "p.value") %>% 
  ggplot(aes(x = p.value)) + geom_histogram(bins = 20) + theme_bw() + facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 100, label = label), color = "black") + 
	theme(strip.text.x = element_text(size=15))

@@

#Adjustment results: Effect difference histograms
effect.diff <- metac %>% mutate(
	est.fixef = ifelse(!is.na(est.fixef.bin), est.fixef - 1, est.fixef),
	est.ranef = ifelse(!is.na(est.fixef.bin), est.ranef - 1, est.ranef),
	est.trimfill.fixef = ifelse(!is.na(est.fixef.bin), est.trimfill.fixef - 1, est.trimfill.fixef),
	est.copas = ifelse(!is.na(est.fixef.bin), est.copas - 1, est.copas),
	est.reg.ranef = ifelse(!is.na(est.fixef.bin), est.reg.ranef - 1, est.reg.ranef),
	fixef.ranef = ifelse(abs(est.ranef) > abs(est.fixef), "Reduction", "Amplification"),
	fixef.trimfill = ifelse(abs(est.fixef) > abs(est.trimfill.fixef), "Reduction", "Amplification"),
	fixef.copas = ifelse(abs(est.fixef) > abs(est.copas), "Reduction", "Amplification"),
	fixef.reg = ifelse(abs(est.fixef) > abs(est.reg.ranef), "Reduction", "Amplification"),
	fixef.trimfill.s = ifelse(sign(est.fixef) == sign(est.trimfill.fixef), "Unchanged", "Reversed"),
	fixef.copas.s = ifelse(sign(est.fixef) == sign(est.copas), "Unchanged", "Reversed"),
	fixef.reg.s = ifelse(sign(est.fixef) == sign(est.reg.ranef), "Unchanged", "Reversed"))

hist.ranef <- effect.diff %>% ggplot(aes(x = abs(est.fixef - est.ranef))) +
	geom_histogram() + facet_grid(~factor(fixef.ranef)) + xlim(0, 2) + xlab("Effect difference") + 
	theme_bw() + theme(legend.position = "bottom", strip.text.x = element_text(size=15)) + ylim(0, 250)

@@

hist.trimfill1 <- effect.diff %>% ggplot(aes(x = abs(est.fixef - est.trimfill.fixef))) +
	geom_histogram() + facet_grid(~factor(fixef.trimfill)) + xlim(0, 2)+ xlab("Effect difference") +
	geom_text(data = trimfill.label, mapping = aes(label = label, x = 0, hjust = 0, y = 300), 
						color = "black") + theme_bw() + 
	theme(legend.position = "bottom", strip.text.x = element_text(size=15))

@@

copas.label$label <- as.character(copas.label$label)
copas.label$label[1] <- sub("3.5,", "3.5, \n   ", copas.label$label[1])
copas.label$label[2] <- sub("11.5,", "11.5, \n   ", copas.label$label[2])

@@

hist.copas1 <- effect.diff %>% filter(!is.na(est.copas)) %>% ggplot(aes(x = abs(est.fixef - est.copas))) +
	geom_histogram() + facet_grid(~factor(fixef.copas)) + xlim(0, 2) + xlab("Effect difference") +
	geom_text(data = copas.label, mapping = aes(label = label, x = 0, hjust = 0, y = 175), 
						color = "black") + theme_bw() +
	theme(legend.position = "bottom", strip.text.x = element_text(size=15))

@@

hist.reg <- effect.diff %>% ggplot(aes(x = abs(est.fixef - est.reg.ranef), fill = factor(fixef.reg.s))) +
	geom_histogram() + facet_grid(~factor(fixef.reg)) + xlim(0, 3)+ xlab("Effect difference") +
	geom_text(data = reg.ranef.label, mapping = aes(label = label, x= 0, y = 250, hjust = 0), 
						color = "black", size = 2.8) + theme_bw() + scale_fill_discrete(name="Effect direction") +
	theme(legend.position = "bottom", strip.text.x = element_text(size=15))

hist.reg1 <- effect.diff %>% ggplot(aes(x = abs(est.fixef - est.reg.ranef))) +
	geom_histogram() + facet_grid(~factor(fixef.reg)) + xlim(0, 3)+ xlab("Effect difference") +
	geom_text(data = reg.ranef.label, mapping = aes(label = label, x= 0, y = 250, hjust = 0), 
						color = "black", size = 2.8) + theme_bw() + 
	theme(legend.position = "bottom", strip.text.x = element_text(size=15))

@@

#Scatterplots of metac-analysis and corrected log(abs(abs estimates
ranef.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.fixef))), y = log(abs(est.ranef)))) + geom_point() + 
	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
	xlab("Fixed effects log estimate") + ylab("Random effects log estimate") + ggtitle("Fixed effects to Random effects")

# metac %>% ggplot(aes(y = log(abs((est.ranef))), x = log(abs(est.trimfill.fixef)))) + geom_point() + 
# 	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
# 	xlab("Random effects log estimate") + ylab("Trimfill log estimate") + ggtitle("Random effects to Trimfill")

@@

#Scatterplots of metac-analysis and corrected log estimates
copas.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.fixef))), y = log(abs(est.copas)))) + geom_point() + 
	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + xlim(0, 25) +
	xlab("Fixed effects log estimate") + ylab("Copas log estimate") + ggtitle("Fixed effects to Copas")

copas.ranef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.ranef))), y = log(abs(est.copas)))) + geom_point() + 
	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE, show.legend = T) + xlim(0, 20) +
	xlab("Random effects log estimate") + ylab("Copas log estimate") + ggtitle("Random effects to Copas")

#Scatterplots of metac-analysis and corrected log estimates
reg.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.fixef))), y = log(abs(est.reg.ranef)))) + geom_point() + 
	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
	xlab("Fixed effects log estimate") + ylab("Regression log estimate") + ggtitle("Fixed effects to Regression")

@@

#Scatterplots of test- statistics:
ranef.fixef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.ranef))) + geom_point() +
	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
	ggtitle("Fixed effects and Random effects z statistics") + ylab("Random effects statistic") + xlab("Fixed effects statistic")

metac %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.trimfill.fixef))) + geom_point() +
	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
	ggtitle("Fixed effects and Random effects z statistics") + ylab("Random effects statistic") + xlab("Fixed effects statistic")

@@

reg.ranef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.ranef), y = abs(zval.reg.ranef))) + geom_point() +
	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
	ggtitle("Random effects and Regression z statistics") + ylab("Regression  statistic") + xlab("Random effects  statistic")

#Missing study proportions:
p.missing.copas <- metac %>% ggplot(aes(x = missing.copas/n)) + geom_histogram(bins = 20) + 
	xlim(0, 0.5) + ylim(0, 200) + xlab("Proportion of missing studies") + ggtitle("Copas selection model") + theme_bw()
p.missing.trim <- metac %>% ggplot(aes(x = missing.trim)) + geom_histogram(bins = 20) + 
	xlim(0, 0.5) + ylim(0, 200) + xlab("Proportion of missing studies") + ggtitle("Trim-and-fill") + theme_bw()
@

@@

\begin{frame}{Publication Bias}
Availability of studies depends on the effect sizes thereof

Thesis topic: Abundancy and extent of publication bias in clinical science
\end{frame}

@@

\begin{frame}{Small Study Effects}
Causes:
\begin{itemize}
\item Selective publication of studies with significant results - publication bias
\item Selective reporting of most favorable outcomes
\item Systematic differences in study settings
\end{itemize}
\end{frame}

\begin{frame}{Small Study Effect Tests}
Different approaches:
\begin{itemize}
\item Simple linear regression
\item Rank correlation
\end{itemize}

Special methods for binary outcomes	
\end{frame}

% \begin{frame}[fragile]{Small Study Effect Tests}
% Funnel plots (continuous outcome examples):
% 
% \vspace{-1.2cm}
% 
% <<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
% par(las = 1, mfrow = c(1, 2))
% funnel(meta.example)
% funnel(meta.nexample)
% @
% 
% \end{frame}
% 
% 
% \begin{frame}[fragile]{Regression based Tests}
% Radial plots (continuous outcome examples):
% 
% \vspace{-1.1cm}
% 
% <<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
% par(las = 1, mfrow = c(1,2))
% biased.rev$inv <- 1/biased.rev$se
% plot(y = (biased.rev$effect/biased.rev$se), x = (biased.rev$se^-1), xlim = c(0, 6), xlab = "inverse standard error", 
% 		 ylab = "mean diff. / std. error")
% 
% unbiased.rev$inv <- 1/unbiased.rev$se
% plot(y = (unbiased.rev$effect/unbiased.rev$se), x = (unbiased.rev$inv), xlim = c(0, 1.2), 
% 		 ylim = c(-18, 0), xlab = "inverse standard error", ylab = "mean diff. / std. error")
% @
% 
% \end{frame}

@@

\begin{frame}[fragile]{Limit Meta-Analysis}
Funnel plot with effect with infinite precision:

@@

\begin{frame}{Selection model}
\citet{Copas1}: model based on a bivariate normal distribution:

@@

\begin{frame}{Trim-and-Fill}
Mirror studies that cause asymmetry:
\vspace{-1.2cm}

<<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
par(las = 1, mfrow = c(1, 2))
funnel(meta.example)
funnel(meta.nexample)
@
\end{frame}

\begin{frame}[fragile]{Results:}
Difference between random and fixed effects meta-analysis estimate:

\vspace{-3mm}
<<echo = FALSE, fig.height = 3.6, message = FALSE, warning=FALSE>>=
plot(hist.ranef)
@
\end{frame}

@@

\vspace{-3mm}
<<echo = FALSE, fig.height = 3.6, message = FALSE, warning=FALSE>>=
plot(hist.trimfill1)
@
\end{frame}

@@

\vspace{-3mm}
<<echo = FALSE, fig.height = 3.6, message = FALSE, warning=FALSE>>=
plot(hist.copas1)
@
\end{frame}

@@

\vspace{-3mm}
<<echo = FALSE, fig.height = 3.6, message = FALSE, warning=FALSE>>=
plot(hist.reg1)
@
\end{frame}

\begin{frame}[fragile]{Results:}
Random and fixed effects meta-analyses test statistics:

\vspace{-3mm} 
<<echo = FALSE, fig.height = 3.8, message = FALSE, warning=FALSE>>=
plot(ranef.fixef.sc.zval)
@
\end{frame}

@@

\vspace{-3mm} 
<<echo = FALSE, fig.height = 3.8, message = FALSE, warning=FALSE>>=
grid.arrange(trimfill.fixef.sc.zval, trimfill.ranef.sc.zval, ncol = 2)
@
\end{frame}

@@

\vspace{-3mm}
<<echo = FALSE, fig.height = 3.8, message = FALSE, warning=FALSE>>=
grid.arrange(copas.fixef.sc.zval, copas.ranef.sc.zval, ncol = 2)
@
\end{frame}

@@

\vspace{-3mm}
<<echo = FALSE, fig.height = 3.8, message = FALSE, warning=FALSE>>=
grid.arrange(reg.fixef.sc.zval, reg.ranef.sc.zval, ncol = 2)
@
\end{frame}

\begin{frame}[fragile]{Adjustment Results}
Missing study proportions:

\vspace{-3mm}
<<echo = FALSE, fig.height = 3.8, message = FALSE, warning=FALSE>>=
grid.arrange(p.missing.copas, p.missing.trim, ncol = 2) 
@
\end{frame}

\begin{frame}[fragile]{Extreme Results}
RR reduction by trimfill (-3.9), side effects

<<echo = FALSE, fig.height = 3.5>>=
trimfill.id(165815)
@
\end{frame}

\begin{frame}[fragile]{Extreme Results}
RR Reduction by copas selection model (-4), pain relief

<<echo = FALSE, fig.height = 3.5>>=
funnel.id(73169)
@
\end{frame}

\begin{frame}[fragile]{Extreme Results}
RR Amplification by regression (+14), side effects

<<echo = FALSE, fig.height = 3.5>>=
limitmeta.id(119537)
@
\end{frame}

\begin{frame}[fragile]{Discussion}
\begin{itemize}
\item Proportion of positive tests is well above 10\%
\item Effect sizes and evidence for treatment effect is diminishued
\item Limitations: not only primary outcomes, adjustment methods known to
perform poorly under the 0
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Outlook}
\begin{itemize}
\item Connect results with different medical fields, look for differences
\item Connect results with single studies and journals (?)
\end{itemize}
\end{frame}

@@

\begin{frame}[fragile]{Results}
log treatment effect estimates:

\vspace{-3mm}
<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
plot(ranef.fixef.sc.effect)
@
\end{frame}
